\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-18 Paper/PaperJahrSchlich.tex
Vorbereitung für Bilder
siehe oben

@@

\usepackage[colorlinks, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}

@@

\begin{figure}
\centering
\setlength\fboxsep{1.5em}\fcolorbox{white}{lightgray}{\includegraphics[scale=0.4]{figures/testsetup.png}}
\caption{Laboratory setup (Source: own photograph)}
\label{fig:teststructure}
\end{figure}

@@

To validate the autonomous sensor fault detection, a sensor fault was simulated by shifting and rotating one of the sensor nodes after completion of the training phase.
The expected magnitudes deviated from the measured magnitudes (\autoref{tab:sensorfault}.
The SHM system recognized the deviation and the boolean was set to "TRUE" accordingly.

>>>>

\usepackage{subcaption}

@@

\usepackage[colorlinks, linkcolor=black, citecolor=blue, urlcolor=blue, bookmarks]{hyperref}

@@

\begin{figure}[htb]

	\centering

	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{figures/testsetup.png}
    	\caption{Regular sensor arrangement}
		\label{fig:teststructure}
    \end{subfigure}
  	\begin{subfigure}{0.49\textwidth}
		\includegraphics[width=\textwidth]{figures/testsetup.png}
    	\caption{Simulated sensor fault}
        \label{fig:sensorfault}
	\end{subfigure}
  	\caption{Laboratory setup (Source: own photographs)}
\end{figure}

@@

To validate the autonomous sensor fault detection, a sensor fault was simulated by shifting and rotating one of the sensor nodes after completion of the training phase.
The expected magnitudes deviated from the measured magnitudes (\autoref{tab:sensorfault}).
The SHM system recognized the deviation and the boolean was set to "TRUE" accordingly.
